Do investors in clean energy ETFs herd?

### 2025-02-20 alt_energy_herding.qmd
vassilas changes

---
format:
  pdf:
    tbl-cap-location: top
    dpi: 500
    fig-pos: "H"
    number-sections: true
    cite-method: natbib
    include-in-header: 
      - text: |
          \usepackage{lscape}
          \newcommand{\blandscape}{\begin{landscape}}
          \newcommand{\elandscape}{\end{landscape}}
          \usepackage{rotating}
          \newcommand{\bsideways}{\begin{sidewaystable}[htbp]}
          \newcommand{\esideways}{\end{sidewaystable}}
      - file: preamble.tex 
    include-before-body: title.tex
    keep-tex: TRUE
  docx:
    reference-doc: new_template_no_numbering.docx
pdf-engine: lualatex
# monofont: "DejaVu Sans Mono"
# mainfont: "Times New Roman"
execute: 
  echo: false
  warning: false
editor: source
bibliography: references.bib
biblio-style: apalike
natbiboptions: round
link-citations: true
linkcolor: blue!100!black
urlcolor: blue!100!black
citecolor: blue!100!black
linestretch: 1.5
indent: TRUE
title-block-banner: false
title-block-style: none
render-on-save: true
---

@@

```{r functions}
source(here("Functions","flextable_word.R" ))
source(here("Functions","modelsummary_word.R" ))
source(here("Functions","modelplot_word.R" ))
source(here("Functions","borderlines.R" ))
source(here("Functions","fx_plot.R" ))
```

@@

Exchange-traded funds (ETFs) are a key feature of green financial products. ETFs are a type of security that involves a collection of securities that often tracks an underlying index. However, they can invest in various industry sectors or strategies. In addition, environment, social, and governance (ESG) ETFs serve as a market discovery tool for investors to identify and invest in environmentally friendly companies [@briere2023]. Among the ESG ETFs, the Clean Energy (CE) ETFs have been the best-performing ones in 2022, followed by the Cybersecurity and Artificial Intelligence (AI) ETFs [@decclesia2024]. The clean energy transition represents one of the largest multi-decade secular growth opportunities.  After the inclusion of Green energy financing in the list of United Nations Sustainability Goals (SDGs) as SDG 7, the role, importance, and visibility of green financial products have escalated enormously [@naqvi2022]. That is, the growth of green assets under management is likely to continue.

@@

Therefore,  this study investigates herding behaviour in alternative energy ETFs in the US between 2019 and 2024. We then demonstrate how climate-related uncertainty can drive herding behaviour in these markets. Methodologically, we follow the standard herding tests by @christie1995 and @chang2000. The traditional approach was supplemented by quantile regressions [@koenker1978 ] in order to capture the time-varying aspects of herding. Lastly,  we extend recent approaches by @bua2024 and others, which seek to establish a link between climate uncertainty and herding behaviour. The next section describes the data and methodology, followed by the results and conclusions.

@@

This study offers novel and valuable insights into herding behaviour in clean energy ETFs. We used various herding behaviour tests to achieve this. First, the baseline herding tests revealed significant evidence of herding behaviour. Second, the asymmetric herding tests showed that herding behaviour was present in both bear and bull markets. Lastly, the results of the time-varying tests point to significant periodic herding. However, the results further indicate that herding in US clean energy ETFs was not mainly related to climate-related risks or uncertainty. The probit analysis showed that climate-related uncertainty reduced the probability of herding or led to investor anti-herding behaviour. We defer to the literature on the factors that drive herding in these ETFs [for example, @loang2023;  @koutmos2024; @przychodzen2016]. Our results, similar to @bua2024, indicate that investors did not herd on climate-related uncertainty, and sought returns whilst hedging against climate-related risk. This is a positive for the financial stability of these growing alternative investment indices.

>>>>

---
format:
  pdf:
    tbl-cap-location: top
    dpi: 500
    fig-pos: "H"
    number-sections: true
    cite-method: natbib
    include-in-header: 
      - text: |
          \usepackage{lscape}
          \newcommand{\blandscape}{\begin{landscape}}
          \newcommand{\elandscape}{\end{landscape}}
          \usepackage{rotating}
          \newcommand{\bsideways}{\begin{sidewaystable}[htbp]}
          \newcommand{\esideways}{\end{sidewaystable}}
      - file: preamble.tex 
    include-before-body: title.tex
    keep-tex: TRUE
  docx:
    reference-doc: new_template_no_numbering.docx
pdf-engine: lualatex
# monofont: "DejaVu Sans Mono"
# mainfont: "Times New Roman"
execute: 
  echo: false
  warning: false
editor: source
bibliography: energy_herding.bib
biblio-style: apalike
natbiboptions: round
link-citations: true
linkcolor: blue!100!black
urlcolor: blue!100!black
citecolor: blue!100!black
linestretch: 1.5
indent: TRUE
title-block-banner: false
title-block-style: none
render-on-save: true
---

@@

```{r functions}
source(here("Functions","flextable_word.R" ))
source(here("Functions","modelsummary_word.R" ))
source(here("Functions","modelplot_word.R" ))
source(here("Functions","borderlines.R" ))
source(here("Functions","fx_plot.R" ))

@@

Exchange-traded funds (ETFs) are a key feature of green financial products. ETFs are a type of security that involves a collection of securities that often tracks an underlying index. However, they can invest in various industry sectors or strategies. In addition, environment, social, and governance (ESG) ETFs serve as a market discovery tool for investors to identify and invest in environmentally friendly companies [@briere2023]. Among the ESG ETFs, the Clean Energy (CE) ETFs have been the best-performing ones in 2022, followed by the Cybersecurity and Artificial Intelligence (AI) ETFs [@decclesia2024]. The clean energy transition represents one of the largest multi-decade secular growth opportunities.  After the inclusion of Green energy financing in the list of United Nations Sustainability Goals (SDGs) as SDG 7, the role, importance, and visibility of green financial products have escalated enormously [@naqvi2022]. That is, the growth of green assets under management is likely to continue. Lastly, the limited availability of data on ESG complying investment tools [@avramov2022; @nguyen2025] justifies the use of green (CE) ETFs as best candidates of green assets.

@@

In addition, our study extends the results of @dragomirescu-gaina2021 who examined herding behavior of investors in the US energy sector and herding sensitivity to various proxies of policy uncertainty and financial risk. They employed the energy equities included in the S&P 500 and concluded that herding among investors in the US energy market sector is sensitive to green volatility shocks

Therefore,  this study investigates herding behaviour in alternative energy ETFs in the US between 2016 and 2024. We then demonstrate how climate-related uncertainty can drive herding behaviour in these markets. Methodologically, we follow the standard herding tests by @christie1995 and @chang2000. The traditional approach was supplemented by quantile regressions [@koenker1978 ] in order to capture the time-varying aspects of herding. Lastly,  we extend recent approaches by @bua2024 and others, which seek to establish a link between climate uncertainty and herding behaviour. The next section describes the data and methodology, followed by the results and conclusions.

@@

This study offers novel and valuable insights into herding behaviour in clean energy ETFs. We used various herding behaviour tests to achieve this. First, the baseline herding tests revealed significant evidence of herding behaviour. Second, the asymmetric herding tests showed that herding behaviour was present in both bear and bull markets. Lastly, the results of the time-varying tests point to significant periodic herding. However, the results further indicate that herding in US clean energy ETFs was not mainly related to climate-related risks or uncertainty. The probit analysis showed that climate-related uncertainty reduced the probability of herding or led to investor anti-herding behaviour. We differ to the literature on the factors that drive herding in these ETFs [for example, @loang2023;  @koutmos2024; @przychodzen2016]. Our results, similar to @bua2024, indicate that investors did not herd on climate-related uncertainty, and sought returns whilst hedging against climate-related risk. This is a positive for the financial stability of these growing alternative investment indices.

### 2025-02-20 alt_energy_herding.tex
vassilas changes

\usepackage{amsmath,amssymb}
\usepackage{setspace}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\usepackage{fontspec}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{colortbl}
\usepackage{hhline}
\newlength\Oldarrayrulewidth
\newlength\Oldtabcolsep
\usepackage{longtable}
\usepackage{array}
\usepackage{hyperref}
\usepackage{float}
\usepackage{wrapfig}
% \usepackage{hyperref}
% \hypersetup{
%     colorlinks,
%     linkcolor={blue!100!black},
%     citecolor={blue!100!black},
%     urlcolor={blue!100!black}
% }
% \usepackage{apacite}
% \usepackage[round]{natbib} 
% \usepackage{graphicx}
% \usepackage{float}
% \usepackage{caption}
% \usepackage[toc,page]{appendix}
% \usepackage{booktabs,caption}
% \usepackage[flushleft]{threeparttable}
% \usepackage{tabularx}
\usepackage{sfmath}
\usepackage{fontspec}
\usepackage[utf8]{inputenc}
\usepackage{siunitx}
\usepackage{amsfonts}
\usepackage{amsmath}
% \usepackage{xcolor}
% \usepackage{scrextend}
% \deffootnote[2em]{2em}{1em}{\textsuperscript{\thefootnotemark}\,}
% \newcolumntype{Y}{>{\centering\arraybackslash}X}
% \usepackage[a4paper]{geometry}
% \usepackage{caption}
% \usepackage[bottom,flushmargin,hang,multiple]{footmisc}
% \usepackage{pdflscape}
% \usepackage[paper=portrait,pagesize]{typearea}
% \usepackage{rotating}
% \usepackage{fullpage}
% \usepackage{tabu}
\usepackage{lscape}
\newcommand{\blandscape}{\begin{landscape}}
\newcommand{\elandscape}{\end{landscape}}
\usepackage{rotating}
\newcommand{\bsideways}{\begin{sidewaystable}[htbp]}
\newcommand{\esideways}{\end{sidewaystable}}
\KOMAoption{captions}{tableheading}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[round]{natbib}
\bibliographystyle{apalike}
\usepackage{bookmark}

@@

Exchange-traded funds (ETFs) are a key feature of green financial
products. ETFs are a type of security that involves a collection of
securities that often tracks an underlying index. However, they can
invest in various industry sectors or strategies. In addition,
environment, social, and governance (ESG) ETFs serve as a market
discovery tool for investors to identify and invest in environmentally
friendly companies \citep{briere2023}. Among the ESG ETFs, the Clean
Energy (CE) ETFs have been the best-performing ones in 2022, followed by
the Cybersecurity and Artificial Intelligence (AI) ETFs
\citep{decclesia2024}. The clean energy transition represents one of the
largest multi-decade secular growth opportunities. After the inclusion
of Green energy financing in the list of United Nations Sustainability
Goals (SDGs) as SDG 7, the role, importance, and visibility of green
financial products; all have escalated enormously \citep{naqvi2022}.
Therefore, the growth of green assets under management is likely to
continue.

However, given how recent the inclusion of climate sustainability
investment decisions is, it is not clear what the actual impact will be
in the long run. In this study specifically, we ask whether the rapid
adoption of CE ETFs could be driven by market fads, or is a fundamental
change in investor behaviour. Investors, for example, can believe that
peers have information about climate risks that they do not, investors
may herd to avoid losses compared to peers, or investors may be
encouraged to herd by the desire to align to climate-related social
values \citep{ciciretti2021, gavrilakis2023, loang2023}. Therefore,
market volatility and crisis, financial performance, and investor
sentiment can drive herding in ESG markets.

@@

However, to the best of our knowledge, no studies exist that focus on
herding behaviour in CE ESGs. This study, therefore, aims to extend the
broader literature on herding behaviour in commodity and energy markets.
Several studies in this area were conducted. For example,
\citet{demirer2013a} conducted a sector study and found herding
behaviour in grains but not in other sectors. Similarly,
\citet{gilbert2010} showed herding behaviour amongst speculators in
non-ferrous commodities. Others did not find evidence of herding in
similar markets. \citet{babalos2015} found significant anti-herding
behaviour in metal commodities futures after the global financial
crisis. \citet{pierdzioch2010} showed that forecasters in oil and metals
markets deviated from the crowd, indicating a rational response to
information. \citet{steen2013} also found no herding behaviour in
international commodity markets. Overall, the literature in this area is
mixed, which indicates scope for further study.

Therefore, this study investigates herding behaviour in alternative
energy ETFs in the US between 2019 and 2024. We then demonstrate how
climate-related uncertainty can drive herding behaviour in these
markets. Methodologically, we follow the standard herding tests by
\citet{christie1995} and \citet{chang2000}. The traditional approach was
supplemented by quantile regressions \citep[ ]{koenker1978} in order to
capture the time-varying aspects of herding. Lastly, we extend recent
approaches by \citet{bua2024} and others, which seek to establish a link
between climate uncertainty and herding behaviour. The next section
describes the data and methodology, followed by the results and
conclusions.

@@

This study offers novel and valuable insights on herding behavior in
clean energy ETFs.

Results of baseline and rolling window analysis points to significant
herding for the whole period and in various instances.

\citet{choi2023} \citet{kuang2021}

@@

\renewcommand{\bibsection}{}
\bibliography{references.bib}

>>>>

\usepackage{amsmath,amssymb}
\usepackage{setspace}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother

@@

\usepackage{fontspec}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{colortbl}
\usepackage{hhline}
\newlength\Oldarrayrulewidth
\newlength\Oldtabcolsep
\usepackage{longtable}
\usepackage{array}
\usepackage{hyperref}
\usepackage{float}
\usepackage{wrapfig}
% \usepackage{hyperref}
% \hypersetup{
%     colorlinks,
%     linkcolor={blue!100!black},
%     citecolor={blue!100!black},
%     urlcolor={blue!100!black}
% }
% \usepackage{apacite}
% \usepackage[round]{natbib} 
% \usepackage{graphicx}
% \usepackage{float}
% \usepackage{caption}
% \usepackage[toc,page]{appendix}
% \usepackage{booktabs,caption}
% \usepackage[flushleft]{threeparttable}
% \usepackage{tabularx}
\usepackage{sfmath}
\usepackage{fontspec}
\usepackage[utf8]{inputenc}
\usepackage{siunitx}
\usepackage{amsfonts}
\usepackage{amsmath}
% \usepackage{xcolor}
% \usepackage{scrextend}
% \deffootnote[2em]{2em}{1em}{\textsuperscript{\thefootnotemark}\,}
% \newcolumntype{Y}{>{\centering\arraybackslash}X}
% \usepackage[a4paper]{geometry}
% \usepackage{caption}
% \usepackage[bottom,flushmargin,hang,multiple]{footmisc}
% \usepackage{pdflscape}
% \usepackage[paper=portrait,pagesize]{typearea}
% \usepackage{rotating}
% \usepackage{fullpage}
% \usepackage{tabu}
\usepackage{lscape}
\newcommand{\blandscape}{\begin{landscape}}
\newcommand{\elandscape}{\end{landscape}}
\usepackage{rotating}
\newcommand{\bsideways}{\begin{sidewaystable}[htbp]}
\newcommand{\esideways}{\end{sidewaystable}}
\KOMAoption{captions}{tableheading}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[round]{natbib}
\bibliographystyle{apalike}
\usepackage{bookmark}

@@

Exchange-traded funds (ETFs) are a key feature of green financial
products. ETFs are a type of security that involves a collection of
securities that often tracks an underlying index. However, they can
invest in various industry sectors or strategies. In addition,
environment, social, and governance (ESG) ETFs serve as a market
discovery tool for investors to identify and invest in environmentally
friendly companies \citep{briere2023}. Among the ESG ETFs, the Clean
Energy (CE) ETFs have been the best-performing ones in 2022, followed by
the Cybersecurity and Artificial Intelligence (AI) ETFs
\citep{decclesia2024}. The clean energy transition represents one of the
largest multi-decade secular growth opportunities. After the inclusion
of Green energy financing in the list of United Nations Sustainability
Goals (SDGs) as SDG 7, the role, importance, and visibility of green
financial products have escalated enormously \citep{naqvi2022}. That is,
the growth of green assets under management is likely to continue.
Lastly, the limited availability of data on ESG complying investment
tools \citep{avramov2022, nguyen2025} justifies the use of green (CE)
ETFs as best candidates of green assets.

However, given how recent the inclusion of climate sustainability in
investment decisions is, it is not clear what the actual impact will be
in the long run. In this study specifically, we ask whether the rapid
adoption of CE ETFs could be driven by market fads, or is a fundamental
change in investor behaviour. Investors, for example, can believe that
peers have information about climate risks that they do not, investors
may herd to avoid losses compared to peers, or investors may be
encouraged to herd by the desire to align to climate-related social
values \citep{ciciretti2021, gavrilakis2023, loang2023}. Therefore,
market volatility and crisis, financial performance, and investor
sentiment can drive herding in ESG markets.

@@

However, to the best of our knowledge, no studies exist that focus on
herding behaviour in CE ESGs. This study, therefore, aims to extend the
broader literature on herding behaviour in commodity and energy markets.
Several studies in this area were conducted. For example,
\citet{demirer2013a} conducted a commodity sectoral study and found
herding behaviour in grains but not in other sectors. Similarly,
\citet{gilbert2010} showed herding behaviour amongst speculators in
non-ferrous commodities. Others did not find evidence of herding in
similar markets. \citet{babalos2015} found significant anti-herding
behaviour in metal commodities futures after the global financial
crisis. \citet{pierdzioch2010} showed that forecasters in oil and metals
markets deviated from the crowd, indicating a rational response to
market information. \citet{steen2013} also found no herding behaviour in
international commodity markets. Overall, the literature in this area is
mixed, which indicates scope for further study.

In addition, our study extends the results of
\citet{dragomirescu-gaina2021} who examined herding behavior of
investors in the US energy sector and herding sensitivity to various
proxies of policy uncertainty and financial risk. They employed the
energy equities included in the S\&P 500 and concluded that herding
among investors in the US energy market sector is sensitive to green
volatility shocks

Therefore, this study investigates herding behaviour in alternative
energy ETFs in the US between 2016 and 2024. We then demonstrate how
climate-related uncertainty can drive herding behaviour in these
markets. Methodologically, we follow the standard herding tests by
\citet{christie1995} and \citet{chang2000}. The traditional approach was
supplemented by quantile regressions \citep{koenker1978} in order to
capture the time-varying aspects of herding. Lastly, we extend recent
approaches by \citet{bua2024} and others, which seek to establish a link
between climate uncertainty and herding behaviour. The next section
describes the data and methodology, followed by the results and
conclusions.

@@

This study offers novel and valuable insights into herding behaviour in
clean energy ETFs. We used various herding behaviour tests to achieve
this. First, the baseline herding tests revealed significant evidence of
herding behaviour. Second, the asymmetric herding tests showed that
herding behaviour was present in both bear and bull markets. Lastly, the
results of the time-varying tests point to significant periodic herding.
However, the results further indicate that herding in US clean energy
ETFs was not mainly related to climate-related risks or uncertainty. The
probit analysis showed that climate-related uncertainty reduced the
probability of herding or led to investor anti-herding behaviour. We
differ to the literature on the factors that drive herding in these ETFs
\citep[for example,][]{loang2023, koutmos2024, przychodzen2016}. Our
results, similar to \citet{bua2024}, indicate that investors did not
herd on climate-related uncertainty, and sought returns whilst hedging
against climate-related risk. This is a positive for the financial
stability of these growing alternative investment indices.

@@

\renewcommand{\bibsection}{}
\bibliography{energy_herding.bib}
